A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-24 paper.tex
beginning N=4

@@

\vspace{-10pt}
\paragraph{Twisting data:}
The classification of orbits of square-zero supercharges in the 4d $\mc N=4$ supersymmetry algebra is the most interesting among the examples we consider in this paper.  We have the following classes. \chris{some comments claiming we'll discuss things above, to be added.  Also this is to revisit after writing the below.}
\begin{itemize}
 \item Rank $(1,0)$ (and $(0,1)$) supercharges.  Such supercharges automatically square to zero, and are holomorphic: indeed they sit inside an $\mc N=1$ subalgebra.  They are compatible with $\SU(2)_- \sub \Spin(4;\RR)$, which can be promoted to a twisting homomorphism from the group $\mr U(2)$ as we say in the 4d $\mc N=1$ section above.
 \item Rank $(2,0)$ (and $(0,2)$) supercharges.  Such supercharges automatically square to zero, and are topological: indeed they sit inside an $\mc N=2$ subalgebra.  They are compatible with any of three possible twisting homomorphisms:
 \begin{enumerate}
  \item The half twisting homomorphism $\phi_{\mr{1/2}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, 1, 1)$.
  \item The Kapustin-Witten twisting homomorphism $\phi_{\mr{KW}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, B)$.
  \item The Vafa-Witten twisting homomorphism $\phi_{\mr{VW}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, A)$.
 \end{enumerate}
 \item Rank $(1,1)$ supercharges.  Such supercharges have three invariant directions, and also sit inside an $\mc N=2$ subalgebra.  Twists by such supercharges are compatible with a twisting homomorphism from $\Spin(2;\RR) \times \Spin(2;\RR)$, but are only $\ZZ/2\ZZ$-graded, as we discussed in the $\mc N=2$ section above.
 \item Rank $(2,1)$ (and $(1,2)$) supercharges.  Such supercharges are topological, and compatible with a twisting homomorphism from $\Spin(2;\RR) \times \Spin(2;\RR)$.
 \item Rank $(2,2)$ square-zero supercharges are topological, and split into two classes.  Generically, such supercharges correspond to perturbatively trivial twisted theories, and are only compatible with $\Spin(2;\RR) \times \Spin(2;\RR)$.  There is a special point of this type which is compatible with Kapustin-Witten twisting homomorphism.
 \item There is also a special rank $(2,2)$ point (the \emph{B-twisting supercharge}) arising by dimensional reduction from the 5d $\mc N=2$ rank 4 supercharge, which is also compatible with the Kapustin-Witten twisting homomorphism.
\end{itemize}

@@

>>>>

\brian{We have not defined the notation $\Omega^{0,\bu}, \Omega^{\bu,\bu}, \Omega^\bu$.}
\brian{Also, define the notation $T^*[-1] {\rm Map}$. }

@@

The 4d $\cN=4$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills. 
It admits $R$-symmetry group $G_R=\Spin(6; \RR)$ under which $W \cong S_+^6$ is the positive semi-spin representation and $W^* \cong S_-^6$.

The classification of orbits of square-zero supercharges in the 4d $\mc N=4$ supersymmetry algebra is the most interesting among the examples we consider in this paper.  
We have the following classes. 
\chris{some comments claiming we'll discuss things above, to be added.  Also this is to revisit after writing the below.}
\begin{itemize}
\item Rank $(1,0)$ and $(0,1)$ supercharges.  
Such supercharges automatically square to zero, and are holomorphic: indeed they sit inside an $\mc N=1$ subalgebra.  
They are compatible with the subgroup $\U(2) \sub \Spin(6;\RR) = \SU(4)$.
 \item Rank $(2,0)$ (and $(0,2)$) supercharges.  Such supercharges automatically square to zero, and are topological: indeed they sit inside an $\mc N=2$ subalgebra.  They are compatible with any of three possible twisting homomorphisms:
 \begin{enumerate}
  \item The half twisting homomorphism $\phi_{\mr{1/2}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, 1, 1)$.
  \item The Kapustin-Witten twisting homomorphism $\phi_{\mr{KW}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, B)$.
  \item The Vafa-Witten twisting homomorphism $\phi_{\mr{VW}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, A)$.
 \end{enumerate}
 \item Rank $(1,1)$ supercharges.  Such supercharges have three invariant directions, and also sit inside an $\mc N=2$ subalgebra.  Twists by such supercharges are compatible with a twisting homomorphism from $\Spin(2;\RR) \times \Spin(2;\RR)$, but are only $\ZZ/2\ZZ$-graded, as we discussed in the $\mc N=2$ section above.
 \item Rank $(2,1)$ (and $(1,2)$) supercharges.  Such supercharges are topological, and compatible with a twisting homomorphism from $\Spin(2;\RR) \times \Spin(2;\RR)$.
 \item Rank $(2,2)$ square-zero supercharges are topological, and split into two classes.  Generically, such supercharges correspond to perturbatively trivial twisted theories, and are only compatible with $\Spin(2;\RR) \times \Spin(2;\RR)$.  There is a special point of this type which is compatible with Kapustin-Witten twisting homomorphism.
 \item There is also a special rank $(2,2)$ point (the \emph{B-twisting supercharge}) arising by dimensional reduction from the 5d $\mc N=2$ rank 4 supercharge, which is also compatible with the Kapustin-Witten twisting homomorphism.
\end{itemize}

@@

We consider a rank $1$ supercharge $Q$ which factors through a $\cN=2$ subalgebra (in fact $\cN=1$ subalgebra).

\begin{theorem}
The holomorphic twist of 4d $\cN=4$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the holomorphic BF theory on $\CC^2_{\rm Dol}$ with the space of fields $T^*[-1] \map(\CC^2_{\rm Dol} , B \fg) = T^*[-1] \higgs_G(\CC^2)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\label{thm:4d4holomorphictwist}
\end{theorem}
\begin{proof}
The $4d \cN=4$ super Yang-Mills theory viewed as a $\cN=2$ theory is $\cN=2$ Yang-Mills theory with matter in the adjoint representation. 
It follows that the twist is given by $T^*[-1] \map(\CC^2 , (\fg \oplus \fg) / \fg)$. 
\brian{Need to be careful about $\U(2)$ action to get Dolbeault stack.}
\end{proof}
